### 2019-02-27 papers/journal/encoding.tex
Partial encoding added

\subsection{SMT based encoding}

@@

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align}
  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
\end{align}
If a molecule is active on an edge, it should be present on the edge.
%
\begin{align}
  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
\end{align}
A molecule should be present to be active on a node.  
\begin{align}
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  \tag{V3}\label{eq:c4}
\end{align}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
\end{align}
Self edges are not allowed. 
\begin{align}
   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
\end{align}
We fix first half as Q-SNAREs and rest as R-SNAREs and set diagonal blocks in pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
\begin{align}
  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
  \tag{V6}\label{eq:c3}
\end{align}

@@

The BMC encoding differs with the presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
%
Variables are not Boolean indexed with multiple dimensions but arrays of bitvectors of size $\mu$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
For example the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
%
The index of the bitvector implicitly determines the corresponding molecule we are referring to.

\begin{enumerate}
	\item Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
\end{enumerate}

%

The molecule set is divided into Q and R-SNAREs. 
%
For clarity, we consider both in the same amount and represent the first half of the bitvector as  Q-SNAREs and rest as R-SNAREs.
%
An edge in the system with M = 4 molecules is interpreted as a tag [M1, M2, M3, M4]. 
%
Where M1, M2 are Q-SNAREs and M3, M4 are R-SNAREs.
%
Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the molecule i.
%

\textbf{Example 1} The variable bv\_e[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule M1 and M4 present.

Similarly, a node in the graph is also tagged as a bitvector of length M.   
%
We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
For clarity, we will only present the stability encoding.

@@

Now we can encode stability using the NOracle and say if there is an $m$-edge between $i$ and $j$, there is a $m$-path from $j$ to $i$ of length max w.
%
We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

>>>>

\subsection{SMT based encoding}
\label{enc:smt}

@@

\subsubsection{Constraints on presence, activity of the molecule, and pairing matrix}
%
We need the following constraints~\eqref{eq:f0} and~\eqref{eq:c3}
to encode the basic structure of VTSs.
%
For an edge to exist it should have one molecule present. 
%
\begin{align}
  \bigwedge\limits_{i,j,q} (\bigvee_m e_{i,j,q,m} )\limplies e_{i,j,q}\tag{V1}\label{eq:f0}
\end{align}
If a molecule is active on an edge, it should be present on the edge.
%
\begin{align}
  \bigwedge\limits_{i,j,q,m} b_{i,j,q,m} \limplies e_{i,j,q,m}\tag{V2}\label{eq:f1}
\end{align}
A molecule should be present to be active on a node.  
\begin{align}
  \bigwedge\limits_{i,m} a_{i,m} \limplies n_{i,m}
  \tag{V3}\label{eq:c4}
\end{align}
The edge labels are subset of the node labels of the source and target nodes.
\begin{align}
  \bigwedge\limits_{i,j,q,m} e_{i,j,q,m} \limplies (n_{i,m} \land n_{j,m} )\tag{V4}\label{eq:c0}
\end{align}
Self edges are not allowed. 
\begin{align}
   \bigwedge\limits_{i,q} \neg e_{i,i,q}\tag{V5}\label{eq:c2}
\end{align}
We divide the pairing matrix into Q-SNAREs and R-SNAREs blocks and set the dependency bits of Q-SNAREs to Q-SNAREs (and similarly R-SNAREs to R-SNAREs) in the pairing matrix to be 0's.
%It reduces the search space.
% Condition on $p_{kk'}$. \ashu{why???} .
%\begin{align}
%  \bigwedge\limits_{(x < M/2 \, \land  \, y < M/2) \lor  (x >= M/2 \land y >= M/2)} \neg p(x,y)
%  \tag{V6}\label{eq:c3}
%\end{align}

\begin{align}
  \bigwedge\limits_{(x < 3M/4 \, \land  \, y < 3M/4) \lor  (x >= 3M/4 \land y >= 3M/4)} \neg p(x,y)
  \tag{V6}\label{eq:c3}
\end{align}

@@

The BMC encoding differs with the presented SMT encoding slightly in the way variables are represented and how we encode reachability.  
%
Variables are not Boolean indexed with multiple dimensions but arrays of bitvectors of size $\mu$. 
%
%We initialize the system with a fixed number of node size (N) and distinct molecular types (M). 
%%
%We use a two-dimensional array variable \textit{Graph}[N][N] to represent the transport graph. The graph variable is set to x, Graph[i][j] = x, if there are exactly x edges between node i and j. 
%\begin{align*}
%graph [i] [j] = x.
%\end{align*}
%
For examplei, the edges are represented as a bitvectors of size M with each bit corresponding to the presence or the absence of the molecule. 
%
The index of the bitvector implicitly determines the corresponding molecule we are referring to.
%
Bit vector $bv\_e[i][j][q]$ represent the $q$th edge between node $i$ and $j$.
%

The molecule set is divided into Q and R-SNAREs. 
%
For clarity, we consider both in the same amount and represent the first half of the bitvector as  Q-SNAREs and rest as R-SNAREs.
%
An edge in the system with M = 4 molecules is interpreted as a tag [M1, M2, M3, M4]. 
%
Where M1, M2 are Q-SNAREs and M3, M4 are R-SNAREs.
%
Also, each $M_i$ can be either 0 or 1, representing the presence or absence of the molecule i.
%
For example, the variable bv\_e[1][2][1] = 1001 represent first edge between node 1 and node 2 with molecule M1 and M4 present.

Similarly, a node in the graph is also tagged as a bitvector of length M.   
%
We leave the graph completely arbitrary and add the constraint to enforce that the graph is k-connected. 
%
Here, we will only present the stability encoding.  
%
Rest of the encoding are similar to that of the presented in~\ref{enc:smt}.

@@

We encode stability using NOracle and if there is an $m$-edge between node $i$ and $j$, there has to be a $m$-path from $j$ to $i$ of length maximum w.
%
%We have used bv $\unrhd$ m to extract the $m^{th}$ bit of the bitvector bv. 
\begin{align}
 \bigwedge\limits_{i,j,m} (\bigvee_{q} bv\_e[i][j][q] \limplies NOracle(m, j, i, w)
  \tag{S2}\label{eq:reachbmc2}
\end{align}

%\begin{align}
% \bigwedge\limits_{i,j,m} (\bigvee_{q} (bv\_e[i][j][q] \unrhd m) > 0) \limplies NOracle(m, j, i, w)
 % \tag{S2}\label{eq:reachbmc2}
%\end{align}
